---
title: "Extract data from power BI pbix file using SQL and R"
author: "Michiel van Dijk"
date: "10/01/2020"
output: html_document
---

I want to extract data from a Power BI pbix file using R. The recently released [pbixr package](https://cran.r-project.org/web/packages/pbixr/vignettes/explore.html) seems to offer the functions to do this but unfortunately there is hardly any documentation on how the extract data tables from a pbix file. I experimented with several functions and managed to retrieve the data tables. However, I fail to extract tables that are generated by Power BI using formulas (e.g. SUM etc). These are marked in Power BI with a calculator symbol in front. 

At the office we have a simple piece of software that works very similar to the pbixr package when linking to and collecting data from a pbix file (i.e. using localhost: correct_port in combination with an SQL command), that is able to extract all data including the Power BI generated ones. This makes me think that this also should be possible by using the pbixr package but perhaps I am wrong. 

Possibly the OlapR package from Microsoft also might do the trick but as this is not freeware and probably needs a specific version of R I do not aim to use it. But I welcome any other approaches to access the content of a pbix file.

A reproducible example:

```{r}
#install.packages("pbixr")
library(pbixr)

# Download example pbix file (also see pbixr vignette)
temp_dir <- "C:/users/dijk158/temp"
dir.exists(temp_dir)
sample_file_name <- "sample_vig.pbix"
path_file_sample <- file.path(temp_dir, sample_file_name)
url_pt1 <- "https://github.com/KoenVerbeeck/PowerBI-Course/blob/"
url_pt2 <- "master/pbix/TopMovies.pbix?raw=true"
url <- paste0(url_pt1, url_pt2)
req <- download.file(url, destfile = path_file_sample, mode = "wb")
```

At this point Power BI should be open and the example file sample_vig.pbix opened.

```{r}
# Find port
connections_open <- f_get_connections()
connections_open$pbix <- gsub(" - Power BI Desktop", "",
                              connections_open$pbix_name)
correct_port <- as.numeric(connections_open$ports)

# Create the connection
connection_db <- paste0("Provider=MSOLAP.8;Data Source=localhost:",
                        correct_port, ";MDX Compatibility=1")

# Read tables
sql_table <- "evaluate TopMovies"
get_tables <- f_query_datamodel(sql_table, connection_db)
names(get_tables)
summary(get_tables)
```

`get_tables` only contains the pure data tables but not the Power BI generated ones such as `Avg Rating`, `Avg Votes`, etc. 