---
title: "Dhaka food systems dashboard"
author: "version 0.0001"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  flexdashboard::flex_dashboard:
    theme: simplex
    vertical_layout: fill
    social: menu
    source_code: embed
runtime: shiny
---

I am in the process of creating an R flexdashboard. The dashboard contains several maps for Bangladesh, which are linked to a (Highcharts) chart that is activated by clicking on a polygon (e.g. region). I am able to make it work for one page. However, if I set it up for two pages, things no longer work. 

It seems that flexdashboard (at least how I set it up) is not able to handle two input\$map_shape_click operations at the same time. At the moment it only works on the first page, while there is no reaction on the second page. Interestingly, the print statement I added indicates that it is actually the second input\$map_shape_click that is actived but resulting in an operation on the first page (?). I welcome any suggestions to solve this.

Below a reproducible example (Note that I omitted the flexdashboard yaml in the example):

```{r global, include = FALSE}
# Packages
library(tidyverse)
library(raster)
library(sf)
library(highcharter)
library(leaflet)
library(htmltools)

# Get data
adm1 <- getData('GADM', country='BGD', level=1)
adm1 <- st_as_sf(adm1)

# Create dummy data.frames with link to polygon
df1 <- data.frame(NAME_1 = adm1$NAME_1,
                 value_1 = c(1:7))

df2 <- data.frame(NAME_1 = adm1$NAME_1,
                 value_2 = c(8:14))
```


Page 1
=======================================================================

Column {data-width=350} 
-------------------------------------

### Map 1

```{r}
# MAIN MAP --------------------------------------------------------------------------------
output$map <- renderLeaflet({

  # Base map
  leaflet() %>%
    addTiles(group = "OpenStreetMap") %>%
    clearShapes() %>%
    addPolygons(data = adm1, 
                smoothFactor = 0, 
                color = "black",
                opacity = 1,
                fillColor = "transparent",
                weight = 0.5,
                stroke = TRUE,
                label = ~htmlEscape(NAME_1),
                layerId = ~NAME_1,
                )
  
})
leafletOutput('map')  


# REGION SELECTION -----------------------------------------------------------------------

# Click event for the map to draw chart
click_poly <- eventReactive(input$map_shape_click, {

  x <- input$map_shape_click
  y <- x$id
  return(y)
}, ignoreNULL = TRUE) 


observe({
  req(click_poly()) # do this if click_poly() is not null

  # Add the clicked poly and remove when a new one is clicked
  map <- leafletProxy('map') %>%
      removeShape('NAME_1') %>%
      addPolygons(data = adm1[adm1$NAME_1 == click_poly(), ],
                  fill = FALSE,
                  weight = 4,
                  color = '#d01010', 
                  opacity = 1, 
                  layerId = 'NAME_1')
  })

```



Column {data-width=350}
-----------------------------------------------------------------------

### Plot 1


```{r}

data <- reactive({

  # Fetch data for the click poly
  out <- df1[df1$NAME_1 == click_poly(), ]
  print("page 1") # print statement to show which click_poly is used
  return(out)
  })


output$plot <- renderHighchart({
  req(data()) # do this if click_poly() is not null
  
  chart <- highchart() %>%
      hc_chart(type = 'column') %>%
      hc_legend(enabled = FALSE) %>%
      hc_xAxis(categories = c('A'),
               title = list(text = 'Title 1')) %>%
      hc_yAxis(title = list(text = 'Value 1')) %>%
      hc_plotOptions(series = list(dataLabels = list(enabled = TRUE))) %>%
      hc_add_series(name = 'Series', 
                    data = c(data()$value_1)) %>%
      hc_add_theme(hc_theme_smpl()) %>%
      hc_colors(c('#d01010'))
  })

highchartOutput('plot')

```


Page 2
=======================================================================

Column {data-width=350}
-------------------------------------

### Map 2

```{r}
# MAIN MAP --------------------------------------------------------------------------------
output$map2 <- renderLeaflet({

  # Base map
  leaflet() %>%
    addTiles(group = "OpenStreetMap") %>%
    clearShapes() %>%
    addPolygons(data = adm1, 
                smoothFactor = 0, 
                color = "black",
                opacity = 1,
                fillColor = "transparent",
                weight = 0.5,
                stroke = TRUE,
                label = ~htmlEscape(NAME_1),
                layerId = ~NAME_1,
                )
  
})
leafletOutput('map2')  


# REGION SELECTION -----------------------------------------------------------------------

# Click event for the map to draw chart
click_poly2 <- eventReactive(input$map_shape_click, {

  x <- input$map_shape_click
  y <- x$id
  return(y)
}, ignoreNULL = TRUE) 


observe({
  req(click_poly2()) # do this if click_poly() is not null

  # Add the clicked poly and remove when a new one is clicked
  map <- leafletProxy('map2') %>%
      removeShape('NAME_1') %>%
      addPolygons(data = adm1[adm1$NAME_1 == click_poly2(), ],
                  fill = FALSE,
                  weight = 4,
                  color = '#d01010', 
                  opacity = 1, 
                  layerId = 'NAME_1')
  })

```



Column {data-width=350}
-----------------------------------------------------------------------

### Plot 2


```{r}

data2 <- reactive({

  # Fetch data for the click poly
  out <- df1[df1$NAME_1 == click_poly2(), ]
  print("page 2") # print statement to show which click_poly is used
  return(out)
  })


output$plot <- renderHighchart({
  req(data2()) # do this if click_poly() is not null
  
  chart <- highchart() %>%
      hc_chart(type = 'column') %>%
      hc_legend(enabled = FALSE) %>%
      hc_xAxis(categories = c('A'),
               title = list(text = 'Title 1')) %>%
      hc_yAxis(title = list(text = 'Value 1')) %>%
      hc_plotOptions(series = list(dataLabels = list(enabled = TRUE))) %>%
      hc_add_series(name = 'Series', 
                    data = c(data2()$value_1)) %>%
      hc_add_theme(hc_theme_smpl()) %>%
      hc_colors(c('#d01010'))
  })

highchartOutput('plot2')

```


